Robust-Adaptive Control of Linear Systems:\\ beyond Quadratic Costs

### 2020-05-28 main.tex
Experimental details

In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$. The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_r = 0.1 I_s$.

@@

\paragraph{Actions}
\paragraph{Reward}
\paragraph{Dynamics}

$
\begin{bmatrix}
\dot{p_x}\\
\dot{p_y}\\
\dot{v_x}\\
\dot{v_y}\\
\end{bmatrix} = 
\begin{bmatrix}
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1 \\
0 & 0 & -\theta_x & 0 \\
0 & 0 & 0 & -\theta_y
\end{bmatrix}
\begin{bmatrix}
{p_x}\\
{p_y}\\
{v_x}\\
{v_y}\\
\end{bmatrix}
+
\begin{bmatrix}
0\\
0\\
{u_x}\\
{u_y}\\
\end{bmatrix}.
$

>>>>

In both experiments, we used $\gamma=0.9$,  $\delta=0.9$ and a planning budget $K=100$. The perturbations were sampled uniformly in $[-0.1, 0.1]^r$ while the measurements are Gaussian with covariance $\Sigma_s = 0.1 I_s$.

@@

The system is described by its position $(p_x,p_y)$ and velocity $(v_x, v_y)$:
\begin{equation*}
x = \begin{bmatrix}
p_x & p_y & v_x & v_y
\end{bmatrix}^\transp
\end{equation*}

It is acted upon by means horizontal and vertical forces $u=(u_x, u_y)\in [-1,1]^2$.
We discretise the action space into four constant controls, for each direction:
\begin{equation*}
\cA = \{(-1, -1), (-1, 1), (1, -1), (1, 1)\}
\end{equation*}

The reward encodes the task of navigating to reach a goal state $x_g$ while avoiding collisions with obstacles: $$R(x) = \delta(x)/(1 + \|x - x_g\|_2),$$  where $\delta(x)$ is $0$ whenever $x$ collides with an obstacle, $1$ otherwise.

\paragraph{Dynamics}
The system dynamics consist in a double integrator, with friction parameters $(\theta_x, \theta_y)$:
$$
\begin{bmatrix}
\dot{p_x}\\
\dot{p_y}\\
\dot{v_x}\\
\dot{v_y}\\
\end{bmatrix} = 
\begin{bmatrix}
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1 \\
0 & 0 & -\theta_x & 0 \\
0 & 0 & 0 & -\theta_y
\end{bmatrix}
\begin{bmatrix}
{p_x}\\
{p_y}\\
{v_x}\\
{v_y}\\
\end{bmatrix}
+
\begin{bmatrix}
0\\
0\\
{u_x}\\
{u_y}\\
\end{bmatrix}.
$$
